An asymptotically normal out-of-sample test based on mixed estimation windows

### 2016-10-17 mixedwindow.tex
[#21] Add separate proof of part 2 of Lemma A3

\begin{proof}[Proof of~\eqref{eq:12}]
TBD
\end{proof}

>>>>

\begin{proof}[Proof of~\eqref{eq:12}]
Note that
\begin{equation*}
  \Big\lvert \WesB \Big\rvert =
  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert H_t \rvert \Bigg).
\end{equation*}
Lemma~\ref{res:a2} implies that the first component converges to
zero in probability, so it suffices to show that the second is
$O_p(1)$. As discussed in the proof of Lemma~\ref{res:a2},
$x_t \varepsilon_{t+1}$ is an $L_2$-mixingale
of size $-1/2$ and
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert H_t \rVert_2
  = O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} t^{-1/2}\Bigg)
\end{equation*}
The last summation is $O(1)$ by Lemma A1 of \citet{Wes:96}, completing
the proof.
\end{proof}
